---
title: "Oct 3rd, 2022"
output: pdf_document
date: '2022-10-03'
---

# Estimation on each time point (m = 1)

```{r, message=FALSE}
require(mixtools)
require(Matrix)
require(splines)
require(gridExtra)
library(dplyr)
library(scales)
require(grid)
source("MDSP(modified).R")
source("oracle.R")

### 
# n : number of identitties
# m : time length
# p.x : dimension of hetergeneous variates
# p.z : dimension of homogeneous variates
# k : number of centers
n=200
m=1
p.x=1
p.z=3
k = 2


set.seed(2022)
# Generate Gamma and Beta
t = seq(1,m)
gamma = matrix(0, ncol = k, nrow = m, byrow = FALSE) 
#c <- 1; a <- 0.5
gamma[,1] <- 0#c *(1/t - a)^2 + 2
gamma[,2] <- 1#0.5 *(1/t - 1)^2

#ymax <- max((c *(1-a)^2 + b)/d, (c *(50-a)^2 + b)/d) + 10

id_center = c(rep(1, n/2), rep(2, n/2))
beta = matrix(NA, nrow = p.x, ncol = n * m)

for (i in 1:n) {
  
  temp =  i + seq( 0, m-1 ) * n
  beta[,temp] = matrix( gamma[,id_center[i]], ncol = m,nrow = p.x, byrow = TRUE)
  
}

#plot(1:n, beta)

#beta <- as.vector(beta)
id <- id_center#unique(sample(which(id_center == 1),n * 0.1))

### Generate Data
X=matrix(rnorm(n*m*p.x), n*m,p.x)
Z=cbind(1, matrix(rnorm(n*m*(p.z-1)),n*m,(p.z-1)))
Y=matrix(NA,nrow =  n * m , ncol = 1)

for (i in 1:(n*m)) {
  
  Y[i,] <- X[i,] %*% beta[,i] + rnorm(1, sd = 0.2)
  
}



```



The estimation accuracy is based on $\lambda/\kappa$, not $\lambda itself$, where $\lambda$ is the paramter for L1 penalty and $\kappa$ is the parameter for the augmented L2 penalty. This statement is from the estimation for $\nu$.

$$
min_{\nu_{ijk}} \quad \frac{1}{2} \| \beta_{ijk}^{(l+1)} - \nu_{ijk} +{\kappa}^{-1}  \|^2 
$$




## Acuuracy

Here I would like to explore the parameter tuning effect of $\lambda$ and $\kappa$. In this case, the iteration still has the fixed iteration step.

```{r}
fit_alg <- MDSP_temporal(Y,X,Z,m=m, l1=1000,kp=1,beta.int  = beta +0.5,
                         id = id, beta.true = beta, label = id_center)

plot(1:n, fit_alg$beta.int, ylim = c(-5,250), col = "blue")
lines(1:n,fit_alg$nu_track[30,], type = "p", col = "red")
lines(1:n,beta, type = "p", col = "green")

```


```{r}
fit_alg <- MDSP_temporal(Y,X,Z,m=m, l1=0.5,kp=1,beta.int  = beta +0.5,
                         id = id, beta.true = beta, label = id_center)

plot(1:n, fit_alg$beta.int, ylim = c(-1,3), col = "blue")
lines(1:n,fit_alg$beta_track[3,], type = "p", col = "red")
lines(1:n,beta, type = "p", col = "green")

```

```{r}
fit_alg <- MDSP_temporal(Y,X,Z,m=m, l1=0.1,kp=1,beta.int  = beta +0.5,
                         id = id, beta.true = beta, label = id_center)

plot(1:n, fit_alg$beta.int, ylim = c(-1,3), col = "blue")
lines(1:n,fit_alg$nu_track[5,], type = "p", col = "red")
lines(1:n,fit_alg$beta_track[5,], type = "p", col = "black")
lines(1:n,beta, type = "p", col = "green")

```


I modify the ADMM algorithm based on our previous discussed idea of changing step, where the $\kappa$ is modified during the iteration.

## Running Time


# Over time points (m > 1)